---
title: "Phylogenenetic analysis"
author: "Magdalena Gontarz Zhassulanbaikyzy Gulzhan"
date: "Thursday, October 06, 2016"
output: pdf_document
---

# Introduction
Phylogenetics is the study of evolutionary relationships among groups of organisms,
which are discovered through molecular sequencing data and morphological data (Wikipedia).
These relationships are presented on phylogenetic trees, which are used for different purposes 
for example to classify species or to examine inference of the spatiotemporal evolution of epidemics.

In this report we included issues of computation of evolutionary distances and construction of phylogenetic trees using different methods  - i.e. Unweighted Pair Group Method with Arithmetic Mean (UPGMA) algorithm and Neighbour-Joining (NJ).

# Part 1. Computation of evolutionary distances

## 1)

## 2)

## 3)

## 4)

## 5)


## 6)

```{r}
data = url("http://membres-timc.imag.fr/Michael.Blum/fasta.Rdata")
load(data)


t = seq(0, 100, 0.1)
p = 0.75 * (1-exp(-4*t/3))
plot(t,p)

```

## 7)


## 8)
```{r}
p_prop = seq(0,1,0.01)
d = -0.75 * log(1-4*p_prop/3)
plot(p_prop,d)
```

# Part 2. Construction of phylogenetic trees

## The UPGMA algorithm

## The NJ algorithm


# Part 3. Construction of phylogenetic trees with R



